% !TEX program = xelatex

\documentclass{wenycv}

% optionally suppress printing the page number
\pagenumbering{gobble}

\begin{document}


%% basic personal info
\name{Wenkang Xu}
\begin{basicinfo}
  \info{\email{wenymedia@gmail.com}}
  \info{\homepage{terminal.im}[https://terminal.im]}
  \info{\github{WenyXu}[https://github.com/wenyxu]}
  % \phone{}
\end{basicinfo}

\section{Experiences}

\cventry{Google Summer of Code 2022}
  {March 2022 -- Fall 2022}
  [Casbin Mentor]
  [\iconlink[\faGithub][Casbin-Mesh/neo]{https://github.com/casbin-mesh/neo}] % TODO: github link
  \begin{itemize}
    \item Leads the development of \textbf{Casbin Neo}(new engine option), a Casbin-compatible engine. \iconlink[\faGithub]{https://github.com/casbin-mesh/neo}
    \item Introduces the Synchronization Adaptive Radix Tree, 2-4x faster than BadgerDB's lock-free version Skip List, and 4-6x faster than Std Sync Map.  \iconlink[\faGithub]{https://github.com/casbin-mesh/neo/issues/10}
    \item Builds the all new expression evaluation system, 2-8x faster than the origin dependency.  \iconlink[\faGithub]{https://github.com/casbin-mesh/neo/pull/54}
    \item Introduces the MVVC(Multi-Version Timestamp Ordering) Index  \iconlink[\faGithub]{https://github.com/casbin-mesh/neo/pull/38}

  \end{itemize}


\section{Open-Source Contributions}

\cventry{Senrok/yadal}
  {Fall 2022 - Now}
  [Yet Another Data Access Layer: Accessing S3, POSIX in the same way.]
  [\iconlink[\faGithub][senrok/yadal]{https://github.com/senrok/yadal}]
  \begin{itemize}
    \item Leads the development of the \textbf{yadal} Project, deeply inspired Databend's OpenDAL and Databricks's Delta lake paper.
  \end{itemize}

\cventry{Casbin Community}
  {September 2020 -- Fall 2022}
  [Casbin-Mesh Maintainer]
  [\iconlink[\faGithub][Casbin-Mesh]{https://github.com/casbin/casbin-mesh}]
  \begin{itemize}
    \item Leads the development of \textbf{Casbin Mesh}, A scalable authorization layer built on Casbin and Raft consensus algorithm.
  \end{itemize}
 
\cventry{Personal Projects}{ \iconlink[\faGithub][WenyXu]{https://github.com/wenyxu}}
\begin{itemize}
  \item \textbf{sync-adaptive-radix-tree} :
  {\small An implementation of the Adaptive Radix Tree with Optimistic Lock Coupling.  \iconlink[\faGithub]{https://github.com/WenyXu/sync-adaptive-radix-tree}}
\end{itemize}

\section{Projects}

\cventry{PingCAP's Talent-plan/TinySQL}
  {July 2022 – September 2022}
  [Minimum Viable Product of TiDB]
  [\iconlink{https://asktug.com/t/topic/902996}]
\begin{itemize}
  \item Completes Join table SQL parser.
  \item Implemented the Online Schema Change based on Google F1 paper.
  \item Introduces Count-Min Sketch.
  \item Implemented the predicate pushdown algorithm for aggregate expression (System-R like optimizer operator).
  \item Implemented the dynamic programming version join reordering algorithm.
  \item Implemented the vectorization for several executors.
  \item Implemented the parallel Hash join \& aggregate algorithm.
  \item Implemented the client-side two-phase commit protocol based on Percolator paper.
\end{itemize}

\cventry{CMU Database Group's Bustub}
  {January 2022 – March 2022}
  [CMU 15-445 Course Project]
  []

\begin{itemize}
  \item Implemented the buffer pool manager based on the LRU replacement mechanism.
  \item Implemented the Extendible Hash table.
  \item Implemented the iterator model exectors.
  \item Implemented the concurrecy control based on lock manager.
\end{itemize}

\cventry{PingCAP's Talent-plan/TinyKV}
  {November 2021 – January 2022}
  [A superset of MIT 6.824 Course Raft-KV Project]
  [\iconlink{https://asktug.com/t/topic/393068}]

\begin{itemize}
  \item Implemented a standalone storage engine.
  \item Implemented Raft Leader election, Log replication, Leader transfer, Configration changing, Peer changing algorithms.
  \item Implemented the KV Store based on Multi-Raft.
  \item Implemented the server-side two-phase commit protocol based on Percolator paper.
\end{itemize}

\section{Skills}

\begin{compactlist}
  \item \textbf{Programming Languages}: Golang, Node.js, C++, Rust, Python 
  \item \textbf{Tech Skills}: Key-Value Storage Systems, Distributed Systems
\end{compactlist}

\end{document}
